NumPy---Array Programming in Python

### 2020-01-31 body.tex
Update Fig. 3
Edit NumPy array section

Many of the array-aware functions, such as summation, support \emph{reductions}: aggregating
results across one or more dimensions of the array.
For example, summing a $n$-dimensional array over $d$ axes results in a
$(n-d)$-dimensional array (Fig.~\ref{fig:array-concepts}e).

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{static/sketches/duck-arrays}
  \caption{\textbf{Interoperability.} \fixme{This figure needs work.}}\label{fig:duck-arrays}
\end{figure}

>>>>

Other array-aware functions, such as \code{maximum}, perform
element-by-element \emph{reductions}, aggregating results across one,
multiple, or all axes of a single array.
For example, summing an $n$-dimensional array over $d$ axes results in a
$(n-d)$-dimensional array (Fig.~\ref{fig:array-concepts}e).

@@

Altogether, the combination of a simple in-memory array
representation, a syntax that closely mimics mathematics, and a
variety of array-aware utility functions forms a productive and
powerfully expressive array programming language.

@@

\begin{figure*}
  \centering
  \includegraphics[width=.9\textwidth]{static/sketches/array_protocol.jpg}
  \caption{\textbf{Interoperability.} \fixme{This figure needs work.}}\label{fig:duck-arrays}
\end{figure*}
